---
title: "Agenda for Joakim’s supervision"
date: "2022-02-02"
draft: false
categories: [""]
runningheader: "Agenda for Joakim’s supervision" 
subtitle: ""
author: "Joakim Frögren"
output:
  tufte::tufte_handout:
    latex_engine: xelatex
tufte::tufte_book:
  citation_package: natbib
  latex_engine: xelatex
bibliography: library.bib
link-citations: no

---

```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```
---

```{r setup, include=FALSE}
library(tufte)
# invalidate cache when the tufte version changes
knitr::opts_chunk$set(cache.extra = packageVersion('tufte'))
options(htmltools.dir.version = FALSE)
```

* Time: 9-10 am
* Zoom link: <https://lu-se.zoom.us/j/61617464801>


## 1. Kappa
Supervisors provide feedback on the draft of the kappa

## 2. Study III
JF gives an update on Study III (panel study article)

## 3. Study IV 
JF gives an update of Study IV and what lies ahead when it comes to this study.

## 4. Timetable 
JF gives an update of how he is planning the time he has left of his PhD studies.

## 5. Individual Study Plan (ISP)
Discussion about JF's ISP and how and when to update it.

## 6. Other questions

## 7. Next supervision

