---
title: "Research group meeting"
date: "2021-04-08"
draft: false
categories: [""]
runningheader: "Research group meeting" 
subtitle: ""
author: "Joakim Frögren"
output:
  tufte::tufte_html: default
  tufte::tufte_handout:
    latex_engine: xelatex
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
bibliography: library.bib
link-citations: no
header-includes:
   - \usepackage{coffee4}

---




```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```
---

```{r setup, include=FALSE}
library(tufte)
# invalidate cache when the tufte version changes
knitr::opts_chunk$set(cache.extra = packageVersion('tufte'))
options(htmltools.dir.version = FALSE)
```

\cofeAm{0.6}{0.9}{45}{-5.5cm}{-9.5cm}
\cofeCm{0.6}{0.5}{12}{-4cm}{-4cm}
\cofeDm{0.1}{0.3}{96}{2.5cm}{-5.5cm}


**Zoom link**: <https://lu-se.zoom.us/j/68548230420>

## Information about a new research group.

## Invitation to suggest actions based on the RQ20 (see attached invitation). 
Internal deadline: Apr 13. The invitation refers to the final report of the RQ20 evaluation, available on [this link](https://portal.research.lu.se/portal/files/95724604/210324_RQ20_Lund_Universitys_Research_Quality_Evaluation_2020.pdf).

## Information about strategic work on the department level.

## Information about migration of web pages and server.

## Other issues.
 
 



