---
title: "Research group meeting"
date: "2021-03-02"
draft: false
categories: [""]
runningheader: "Research group meeting" 
subtitle: ""
author: "Joakim Frögren"
output:
  tufte::tufte_html: default
  tufte::tufte_handout:
    latex_engine: xelatex
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
bibliography: library.bib
link-citations: no
header-includes:
   - \usepackage{coffee4}

---




```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```
---

```{r setup, include=FALSE}
library(tufte)
# invalidate cache when the tufte version changes
knitr::opts_chunk$set(cache.extra = packageVersion('tufte'))
options(htmltools.dir.version = FALSE)
```

\cofeAm{0.6}{0.9}{45}{-5.5cm}{-9.5cm}
\cofeCm{0.6}{0.5}{12}{-4cm}{-4cm}
\cofeDm{0.1}{0.3}{96}{2.5cm}{-5.5cm}

## Information about new co-workers in the group.
Kiran introduced herself to the group.

## Information about new research funding.
SS declared that he had received funding from Kampradsstiftelsen. This is funding related to PhD student JO:s fourth stady and Kiran will also take part of that money for her research. AMF also received money from Kampradstiftelsen.

## Update on strategic work within the department.
SI explained that there has been an initiative from the head of the department, to put together three groups that should discuss strategic matters. SI is part of the group providing strategic plan to *research*. There are 5-6 people in SI:s group, they have had a couple of meetings. Than there is another group related to how research groups are formed. Not ideal today the way groups are formed. Most groups are mono-disciplinary. Then there is a third group as well, more directed  towards education. Going to deliver a report to the department board by mid-April. 

This initiative relates to the working environment. Faculty want to see a future director (prefekt) ^[The position is right now vacant and there are struggles trying to find a candidate] who can also lead the way for research, so I think that the work groups. But SI does not see who the situation towards finding a new prefekt will be any different in a number of months.



## Discussion about matters related to our work situation.

OJ explained that he had been to a meeting discussing Forum Medicum.

Not activity-based working, but everyone has their own desk. At each floor there are desks for 34 people. Open areas for 20-30 people. The suggestion is that there should be personal storage spaces in relation to these desks.

SI encouraged us to engage in this matter and keep in contact with OJ because since right now important decisions are being made. The new Vice Chancellor have written (guessed) that onwards people will work around 50% from home. 

OJ explained that the building was planned for activity-based learning. But the opinion has changed in that matter.

MN recommended that we need to look through what we can bring, because there will be limited space for binders and books at Forum Medicum. 

SI explained that there has been an initiative from the head of the
department, to put together three groups that should discuss strategic
matters. SI is part of the group providing strategic plan to
\emph{research}. There are 5-6 people in SI:s group, they have had a
couple of meetings. Than there is another group related to how research
groups are formed. Not ideal today the way groups are formed. Most
groups are mono-disciplinary. Then there is a third group as well, more
directed towards education. Going to deliver a report to the department
board by mid-April.

This initiative relates to the working environment. Faculty want to see
a future director (prefekt)\footnote{The position is right now vacant
  and there are struggles trying to find a candidate} who can also lead
the way for research, so I think that the work groups. But SI does not
see who the situation towards finding a new prefekt will be any
different in a number of months.

\cofeDm{0.3}{0.4}{90}{-5cm}{-7cm}

\hypertarget{discussion-about-matters-related-to-our-work-situation.}{%
\subsection{Discussion about matters related to our work
situation.}\label{discussion-about-matters-related-to-our-work-situation.}}

OJ explained that he had been to a meeting discussing Forum Medicum.

Not activity-based working, but everyone has their own desk. At each
floor there are desks for 34 people. Open areas for 20-30 people. The
suggestion is that there should be personal storage spaces in relation
to these desks.

SI encouraged us to engage in this matter and keep in contact with OJ
because since right now important decisions are being made. The new Vice
Chancellor have written (guessed) that onwards people will work around
50\% from home.

OJ explained that the building was planned for activity-based learning.
But the opinion has changed in that matter.

MN recommended that we need to look through what we can bring, because
there will be limited space for binders and books at Forum Medicum.

SI explained that there has been an initiative from the head of the
department, to put together three groups that should discuss strategic
matters. SI is part of the group providing strategic plan to
\emph{research}. There are 5-6 people in SI:s group, they have had a
couple of meetings. Than there is another group related to how research
groups are formed. Not ideal today the way groups are formed. Most
groups are mono-disciplinary. Then there is a third group as well, more
directed towards education. Going to deliver a report to the department
board by mid-April.

\cofeBm{0.6}{0.9}{78}{-5.5cm}{-9.5cm}

This initiative relates to the working environment. Faculty want to see
a future director (prefekt)\footnote{The position is right now vacant
  and there are struggles trying to find a candidate} who can also lead
the way for research, so I think that the work groups. But SI does not
see who the situation towards finding a new prefekt will be any
different in a number of months.

\hypertarget{discussion-about-matters-related-to-our-work-situation.}{%
\subsection{Discussion about matters related to our work
situation.}\label{discussion-about-matters-related-to-our-work-situation.}}

OJ explained that he had been to a meeting discussing Forum Medicum.

Not activity-based working, but everyone has their own desk. At each
floor there are desks for 34 people. Open areas for 20-30 people. The
suggestion is that there should be personal storage spaces in relation
to these desks.

\cofeBm{0.4}{0.9}{78}{-7.5cm}{8.5cm}
\cofeCm{0.6}{0.5}{12}{-4cm}{-10cm}

SI encouraged us to engage in this matter and keep in contact with OJ
because since right now important decisions are being made. The new Vice
Chancellor have written (guessed) that onwards people will work around
50\% from home.

OJ explained that the building was planned for activity-based learning.
But the opinion has changed in that matter.

MN recommended that we need to look through what we can bring, because
there will be limited space for binders and books at Forum Medicum.









